### 2013-10-22 article.tex
Added draft for abstract.

% ABSTRACT
\Abstract{
\ldots \\
As such, the hypothesis suggested in this proposal may be summarized as follows:
%\quote{\textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}}
%^ Not a valid hypothesis. No sources indicate that WARP has lesser precision.
% Background	(what)
%	Vilket sammanhang utgör studiens bakgrund?
% Challenge		(why)
%	Vilka utmaningar omfattar studien?
% Approach		(how)
%	Vilken ansats tillämpas i studien?
% Results 		(what)
%	Vilka resultat gav studien?
}

@@

>>>>

% ABSTRACT
\Abstract{
Emulation of \textit{GPU}-kernels on the \textit{CPU} is common for the purposes of debugging or profiling, but also in situations where hardware implementations are unavailable, such as server-side applications. When performing such emulation, one may experience severe performance loss due to the architectural differences in-between the two target platforms. This study examines the performance of such emulated kernels, by analyzing three driver types from the \textit{DirectX}-framework using \textit{DirectCompute}, amongst which is the high speed software~rasterizer Microsoft~\textit{WARP}.\\
This study reasons that performance losses traditionally obstructing \textit{GPU}-kernel emulation may be amended sufficiently by technologies such as Microsoft~\textit{WARP} to the degree that such emulation can be considered viable for use in retail applications.\\
As such, the hypothesis suggested in this proposal may be summarized as follows:
\quote{WARP is fast.}
% \textit{The performance of an emulated GPGPU-kernel on a CPU may have it’s performance substantially improved in exchange for some computational precision.}
%^ Not a valid hypothesis. No sources indicate that WARP has lesser precision.
% Background	(what)
%	Vilket sammanhang utgör studiens bakgrund?
% Challenge		(why)
%	Vilka utmaningar omfattar studien?
% Approach		(how)
%	Vilken ansats tillämpas i studien?
% Results 		(what)
%	Vilka resultat gav studien?
}

@@

%\begin{table}[h]
%\begin{center}
%\begin{tabular}{l|r|r|}
%\cline{2-3}
%\multicolumn{1}{c}{\textit{INT}}    & \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
%\multicolumn{1}{|l|}{\textbf{HARD}} &                                      &                                      \\ \hline
%\multicolumn{1}{|l|}{\textbf{SOFT}} &                                      &                                      \\ \hline
%\multicolumn{3}{l}{}                                                                                              \\ \cline{2-3} 
%\multicolumn{1}{c}{\textit{FLOAT}}  & \multicolumn{1}{|c|}{\textbf{BASIC}} & \multicolumn{1}{|c|}{\textbf{TILED}} \\ \hline
%\multicolumn{1}{|l|}{\textbf{HARD}} &                                      &                                      \\ \hline
%\multicolumn{1}{|l|}{\textbf{SOFT}} &                                      &                                      \\ \hline
%\end{tabular}
%\end{center}
%\caption{-}
%\label{tab:conclusion:perc}
%\end{table}
